The Name of the Title is Hope

### 2023-07-28 input/3_related_work.tex
Updates from Overleaf

\section{Related Work}
%intro
In a simplified world, intentional movements directly leading to external events provide a strong sense of responsibility and control over the action's outcome. For instance, when we press a piano key, it is unequivocally clear that we are the ones performing and causing the action. However, the introduction of technology can complicate this relationship. Imagine playing a computer game where a key press controls an avatar playing the piano. The avatar's movement is now generated by a computer, blurring the lines between the performer and the cause of the action. Despite this complexity, research (sources to be provided, such as wn and Imamizu) suggests that as long as the button press and the avatar's movement remain consistent, we still feel a sense of control.

This lingering sense of control might be due to our intentions being reflected in the resulting action (sources needed). However, in augmented interactions, the dynamics change. When technology moves our fingers, our body performs the action, but we may experience a diminished feeling of causing the action [sources - augmented actions lead to less agency; check Yoshi und Harrard 2013, Moore, Wegner und Harrard 2009, Haggard, Clark 2002].

% why is feeling of control important
Because the feeling of control is related to (check for sources on learning effects etc.), understanding the reason for its loss in augmented interactions is relevant.

%theorie 
Sense of agency is simplictily explained within the framework of motor control (see Frith and collegus 2000). When we perform an action without any external interference, the sensory consequences of that action align with the predicted sensory consequences, which are based on a copy of motor commands (i.e., efference copy). However, in situations where the movement is elicited by an external cause, as in augmented actions, the predicted sensory consequences may differ or be absent altogether. In such cases, the actual sensory feedback does not match the predicted sensory feedback.

According to this account, the feeling of agency arises only when the predicted sensory feedback perfectly corresponds to the actual sensory feedback. In other words, when our actions and their outcomes align seamlessly, we experience a sense of agency over those actions.

\begin{figure}[h]
  \centering
  \includegraphics[]{figures}
   \caption{}
  \Description{
}
  \label{fig:com_model}
\end{figure}
(see Carruthers 2012 for a summary of arguments against this model)

>>>>

\section{Related Work}

%Theories of sense of agency + example
The most widely used theory on the sense of agency is the comparator model. It states that our brain when we perform a voluntary, intentional action, generates a sensory prediction, which is compared to the actual sensory feedback received from the sensory system. If the comparison reveals no sensorimotor incongruency, a sense of agency arises (sources). Imagine pressing the key of a piano to produce a tone. In such simple interaction, it is unequivocally clear that we are the ones performing the movement and causing the tone. We experience authorship.

This straightforward relationship is complicated by the introduction of technology. Think about, playing a computer game where a key press controls an avatar playing the piano. Here, we do not really press the piano key, the avatar's movement, and the tone are now generated by a computer. Despite the blurring lines between the performer and the cause of the tone, we still feel a sense of authorship when the comparison does not reveal incongruency. This lingering feeling of control is thought to be elicited by our intentions being reflected in the resulting action (sources needed).

In situations without intentional action, our brain does not generate predictions. Thus, in alignment with the cooperator model, researchers generally measured a lower sense of agency when actions were externally triggered (e.g., by brain simulation (Haggard and Clark, 2002), the body part being moved by another person (Kühn 2013). Accordingly, playing a tune on a piano with technology causes our figure movement, our body performs the action but we do not have the intention to play. We will most likely will lack a sense of agency.

However, action augmentation technology using motor actuation aims to augment the user’s actions diminishing the SoA (see Cornelio 2022).

%old
- %intro
In a simplified world, intentional movements directly leading to external events provide a strong sense of responsibility and control over the action's outcome. For instance, when we press a piano key, it is unequivocally clear that we are the ones performing the movement and causing the tone. However, the introduction of technology can complicate this relationship. Imagine playing a computer game where a key press controls an avatar playing the piano. The avatar's movement is now generated by a computer, blurring the lines between the performer and the cause of the tone. Despite this complexity, research (sources to be provided, such as wn and Imamizu) suggests that as long as the button press and the avatar's movement remain consistent, we still feel a sense of authorship over the tone as a consequence of our action. This lingering sense of control might be due to our intentions being reflected in the resulting action (sources needed).

In augmented interactions, the dynamics change. When technology moves our fingers, our body performs the action, but we may experience a diminished feeling of causing the action [sources - augmented actions lead to less agency; check Yoshi und Harrard 2013, Moore, Wegner und Harrard 2009, Haggard, Clark 2002].

- no intentional binding when action is triggerd by brain stimulation  (Haggard, P., Clark, S. & Kalogeras, J. Voluntary action and conscious awareness. Nat. Neurosci. 5, 382–385 (2002).
- 
The feeling of agency seems to be

However, now  Imagine playing a computer game where a key press controls an avatar playing the piano. The avatar's movement is now generated by a computer, blurring the lines between the performer and the cause of the tone. Despite this complexity, research (sources to be provided, such as wn and Imamizu) suggests that as long as the button press and the avatar's movement remain consistent, we still feel a sense of authorship over the tone as a consequence of our action.

%old 
A sense of agency is the feeling of intentional actions and their external consequences (Haggard, 2017).
It is implicitly explained within the framework of motor control (see Frith and collegus 2000). When we perform an action without any external interference, the sensory consequences of that action align with the predicted sensory consequences, which are based on a copy of motor commands (i.e., efference copy). However, in situations where the movement is elicited by an external cause, as in augmented actions, the predicted sensory consequences may differ or be absent altogether. In such cases, the actual sensory feedback does not match the predicted sensory feedback.

According to this account, the feeling of agency arises only when the predicted sensory feedback perfectly corresponds to the actual sensory feedback. In other words, when our actions and their outcomes align seamlessly, we experience a sense of agency over those actions (see figure \ref{fig:com_model}.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/augmented_com_model_draft.png}
    \caption{draft - visualization of comparator model of the sense of agency in the case of augmented interactions (inspired by Dewey 2019)}
    \label{fig:com_model}
\end{figure}
(see Carruthers 2012 for a summary of arguments against this model)

% relevance of sense of agency
- motor learning ( check Wen, W. et al. Perception and control: individual difference in the sense of agency is associated with learnability in sensorimotor adaptation. Sci. Rep. 11 , 20542 (2021).)

### 2023-07-28 input/7_discussion.tex
Updates from Overleaf

>>>>

% playful experiences: EMS

\begin{comment}
% critics on the intentional binding as a measure of agency
- Recently, the adequacy of the intentional binding paradigm as a measure of agency is questioned.
- see Suzuki 2019, Gutzeit 2023, Hoerl 2020

% snippets that might be useful
- a sense of agency is not an infallible reproduction of objective reality / can be quite divorced from objective reality (see Moore 2016) // --> if people still report agency, in no-intent (only EMS) condition

%future work / relevance of work
- relevance of research for prostheses ( see https://link.springer.com/chapter/10.1007/978-3-030-38740-2_8)
\end{comment}
